Supporting Information:\\Inverse conformational selection in lipid-protein binding

### 2021-07-12 manuscriptPGPEsuppl.tex
Updates from Overleaf

\author{\small Am{\'e}lie Bacle}
\affiliation{\tiny Laboratoire Coop\'{e}ratif "Lipotoxicity and Channelopathies - ConicMeds", Universit\'{e} de Poitiers, 1 rue Georges Bonnet, 86000 Poitiers, France }

\author{Pavel Buslaev}
\affiliation{Nanoscience Center and Department of Chemistry, University of Jyväskylä, P.O. Box 35, 40014 Jyväskylä, Finland}
\affiliation{Research Center for Molecular Mechanisms of Aging and Age-related Diseases, Moscow Institute of Physics and Technology, 141701 Dolgoprudny, Russia}

\author{Rebeca Garc{\'i}a Fandi{\~n}o}
\affiliation{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela, E-15782 Santiago de Compostela, Spain}
\alsoaffiliation{CIQUP, Centro de Investigação em Qu\'{i}mica, Departamento de Qu\'{i}mica e Bioqu\'{i}mica, Faculdade de Ciências, Universidade do Porto, Porto, Portugal}

\author{Fernando Favela-Rosales}
\affiliation[Tecnol\'{o}gico Nacional de M\'{e}xico]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico, ITS Zacatecas Occidente, M\'{e}xico}

\author{Tiago Ferreira}
\affiliation{Halle, Germany}

\author{Patrick F.J. Fuchs}
\affiliation{Sorbonne Universit\'{e}, Ecole Normale Sup\'{e}rieure, PSL University, CNRS, Laboratoire des Biomol\'{e}cules (LBM), 75005 Paris, France}
\alsoaffiliation{Universit\'{e} de Paris, UFR Sciences du Vivant, 75013, Paris, France}

@@

\author{Matti Javanainen}
\affiliation[Czech Academy of Sciences]{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}

@@

\author{Jesper J. Madsen}
\affiliation[University of Chicago]{Department of Chemistry, The University of Chicago, Chicago, Illinois, United States of America}
\alsoaffiliation[University of South Florida]{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, United States of America}

\author{Josef Melcr}
\affiliation[Czech Academy of Sciences]{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}
\alsoaffiliation{Groningen Biomolecular Sciences and Biotechnology Institute 
and The Zernike Institute for Advanced Materials, 
University of Groningen, 9747 AG Groningen, The Netherlands}

\author{Paula Milán Rodríguez}
\affiliation{Sorbonne Université, Ecole Normale Supérieure, PSL University, CNRS, Laboratoire des Biomolécules (LBM), 75005 Paris, France}

\author{Markus S. Miettinen}
% \affiliation[Max Planck Institute of Colloids and Interfaces]{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}

@@

\author{Chris G. Papadopoulos}
\affiliation{Université Paris-Saclay, CEA, CNRS, Institute for Integrative Biology of the Cell (I2BC), 91198, Gif-sur-Yvette, France}

\author{Antonio Pe{\'o}n}
\affiliation{CIQUP, Centro de Investigação em Qu\'{i}mica, Departamento de Qu\'{i}mica e Bioqu\'{i}mica, Faculdade de Ciências, Universidade do Porto, Porto, Portugal}

\author{Thomas J. Piggot}
\affiliation[University of Southampton]{Chemistry, University of Southampton, Highfield, Southampton SO17 1BJ, United Kingdom}

@@

\title{ Supporting Information:\\Conformational plasticity of lipid headgroups in cellular membranes and protein--lipid complexes}

>>>>

\author{Am{\'e}lie Bacle}
\affiliation{\tiny Laboratoire Coop{\'e}ratif "Lipotoxicity and Channelopathies - ConicMeds", Universit{\'e} de Poitiers, 1 rue Georges Bonnet, 86000 Poitiers, France }

\author{Pavel Buslaev}
\affiliation{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, P.O. Box 35, 40014 Jyv{\"a}skyl{\"a}, Finland}
\affiliation{Research Center for Molecular Mechanisms of Aging and Age-related Diseases, Moscow Institute of Physics and Technology, 141701 Dolgoprudny, Russia}

\author{Rebeca Garc{\'i}a Fandi{\~n}o}
\affiliation{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela, E-15782 Santiago de Compostela, Spain}
\affiliation{CIQUP, Centro de Investigação em Qu{\'i}mica, Departamento de Qu{\'i}mica e Bioqu{\'i}mica, Faculdade de Ci{\^e}ncias, Universidade do Porto, Porto, Portugal}

\author{Fernando Favela-Rosales}
\affiliation{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, M\'{e}xico}

\author{Tiago M. Ferreira}
\affiliation{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg, 06120 Halle (Saale), Germany}

\author{Patrick F.J. Fuchs}
\affiliation{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), 75005 Paris, France}
\affiliation{Universit{\'e} de Paris, UFR Sciences du Vivant, 75013, Paris, France}

@@

\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry of the 
Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2, CZ-16610 Prague 6, Czech Republic}

@@

\author{Jesper J. Madsen}
\affiliation{Department of Chemistry, The University of Chicago, Chicago, Illinois, United States of America}
\affiliation{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, United States of America}

\author{Josef Melcr}
\affiliation{Groningen Biomolecular Sciences and Biotechnology Institute 
and The Zernike Institute for Advanced Materials, 
University of Groningen, 9747 AG Groningen, The Netherlands}

\author{Paula Mil{\'a}n Rodr{\'i}guez}
\affiliation{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), 75005 Paris, France}

\author{Markus S. Miettinen}
\affiliation{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
% \affiliation[Max Planck Institute of Colloids and Interfaces]{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}

@@

\author{Chris G. Papadopoulos}
\affiliation{Universit{\'e} Paris-Saclay, CEA, CNRS, Institute for Integrative Biology of the Cell (I2BC), 91198 Gif-sur-Yvette, France}

\author{Antonio Pe{\'o}n}
\affiliation{CIQUP, Centro de Investigação em Qu{\'i}mica, Departamento de Qu{\'i}mica e Bioqu{\'i}mica, Faculdade de Ci{\^e}ncias, Universidade do Porto, Porto, Portugal}

\author{Thomas J. Piggot}
\affiliation{Chemistry, University of Southampton, Highfield, Southampton SO17 1BJ, United Kingdom}

@@

\title{ Supporting Information:\\Inverse conformational selection in lipid-protein binding}
